A quantitative framework for investigating the reliability of empirical network construction

### 2019-02-21 manuscript/reply_to_reviewers_2.tex

		\begin{refquote}

			I think the authors miss one key discomfort with empirical bayes. It seems vaguely anti-ecology, because it assumes that we can L289 : “use information from abundant and easily-sampled species to predict interaction probabilities for species which were observed only rarely.”  A common goal in network ecology is to describe interaction frequencies by using niche-based proxies (phylogeny, traits, etc). If it was a simply a matter that most networks had the same degree distribution, then predicting networks would be much easier than it is. In fact, we are really bad at predicting pairwise interactions (see Olito and Fox), even when we get the emergent structure of the network correct. Yet empirical bayes assumes a kind of commonality among all networks to help narrow the posteriors. I think the authors need to speak to this concern.

		\end{refquote}

		\textbf{R:} We do not share the Reviewer's highly negative view of empirical Bayes. Perhaps this is a matter of perspective: the Reviewer's work seems to focus on a system where a great deal of information about the traits structuring interactions is known and trait values are available for almost all species. In such a system it is absolutely best to use a trait-based model to predict interactions. This is why we began our section on informative priors with trait-based models and only introduce empirical and approximate Bayes as solutions where trait information/models are lacking or where over-fitting is a strong concern. Most of the authors of this manuscript are more used to such relatively information-poor systems. In these cases, we agree that empirical Bayes is not perfect but argue that it is much better than nothing (or an uninformative prior, as long as a somewhat similar network is available).

		The Jeffreys prior gives a maximum likelihood estimate of 0.5 for the probability of an interaction between two species which have never been observed together. Based on our understanding of ecological systems, this seems highly unlikely. Certainly species differ in many ways, but they also do have some similarities, such as limited foraging time and somewhat consistent morphologies. Because of behavioural, morphological, or temporal limits to the number of partners with which a given species can interact, most ecological networks are sparse and most well-sampled species interact with only a small subset of their potential partners (extreme generalists in highly nested mutualistic networks being a notable exception). We can therefore reasonably expect that a species entering a new habitat, for example, will interact with far fewer than half of the available partners. If we do not know which traits strongly affect interactions involving the focal species, or if those traits are not known for all of the species in the network, we cannot use a trait-based model to predict interaction frequencies. This leaves empirical and approximate Bayes as the only viable options unless we are willing to revert to the assumption that unobserved interactions never occur. Certainly empirical Bayes is not perfect, but we are strongly confident that it is still gives more reasonable expectations than ignoring the ecological networks literature.

		Moreover, while we agree that empirical Bayes does not take differences in niche proxies into account, this may not be crucial in all studies. Researchers are often more interested in the overall structure of the network or in some emergent property such as stability than in the relationships between niche proxies and interaction frequencies. In such cases, the number of additional interactions we expect to be observed with further sampling is likely more important than the exact identity of those interactions, and an empirical Bayes approach is reasonable if a good trait-based model and trait information or not available.

		Finally, we must disagree with the Reviewer's contention that ``empirical Bayes assumes a kind of commonality among all networks". This is not so; empirical Bayes only assumes some commonality between the focal network and those used to construct the prior. We have revised the text to emphasize the need to use similar networks to construct an empicial Bayes prior and note that \emph{Appendix S7} demonstrates the pitfalls of basing an empirical Bayes prior on a network with little commonality with the focal system.

		We believe that including an expanded reference to \emph{Appendix S7} as suggested below will help to address some of these concerns by demonstrating that empirical Bayes should \emph{not} be based on networks which have major differences from the focal system as this will lead to unreasonable predictions (in our case, although the taxa and interaction types involved were similar, the taxonomic resolution in the \citet{Barbour2016} and \citet{Kopelke2017} were very different). To reinforce this point and make the role of empirical Bayes as a solution in the absence of trait-based models and/or trait information, we have made several minor revisions to the section introducing informative priors. We hope that these changes will be sufficient to illustrate the drawbacks to empirical Bayes without being overly discouraging for those who lack the necessary information to construct more detailed informative priors.

@@

		\begin{quotation}

			Alternatively, if information on the traits affecting interaction probabilities is lacking, one can develop a prior based on the properties of a set of published networks (``empirical" or ``reference Bayes"~\citet{Spiegelhalter2000}). This type of prior does not vary between species pairs but entails only one assumption: that the focal network has similar structural properties to those of some published networks.

		In lines XX-XX we explicitly state that the networks used to build an empirical Bayes prior should be similar to the focal system:

			The distribution of published connectances can be used to predict the distribution of interaction probabilities in a new network that is similar to those used to construct the prior (same type of interaction, similar taxonomic resolution, habitat, etc.).

		In lines XX-XX we reiterate the fact that an empirical Bayes prior does not vary between pairs of species and that the networks used to build the prior should be similar to the focal network:

		Note that here the prior distribution will be the same for all interaction probabilities. It is also possible to interpret other network properties (e.g., species degrees) in a similar network(s) as interaction probabilities and use these to create a prior (worked example in \emph{Appendix S4}).

### 2019-02-21 manuscript/reply_to_reviewers_2.tex

	\begin{refquote}

		Thank you for the extensive and detailed reply to the comments of the referees. Your revised manuscript was sent back to one of the referees who reviewed the original version. As you will see, he is very positive about the revised version and has now signed his review. The only outstanding issue is the addition of some discussion about how to detect potential problems with the priors. I agree with this suggestion as one of the most common criticisms of Bayesian methods is precisely the use of priors.

	\end{refquote}

	\textbf{R:} We appreciate the additional comments from the Referee, and agree that prior detection can be quite a challenge. We are therefore quite happy to add to our discussion about how to detect potential problems. Note, however, that after making the additions requested by the previous round of reviews our manuscript was very close to the standard word limit for \textbf{Methods in Ecology and Evolution}. To meaningfully expand our discussion of how to detect problems with priors we must therefore ask for more space. We have kept our addition to the discussion as succinct as possible, and the revised manuscript is now approximately 7433 words. We hope that this additional length is justified by our efforts to address the Reviewer's remaining concerns.

@@

		\textbf{R:} We thank the Reviewer for his complement to Figure 3. Although we wish to keep any additions as brief as possible, we are happy to add a short reference to Figure 3 in the discussion as part of an example of how to use our simple Bayesian framework when thinking about insects moving into new communities (e.g., as climate changes). We hope that this puts the figure in a more central place, as intended. We also now include a similar figure demonstrating the effect of a change in prior on the posterior pdf's obtained for the \emph{Salix}-galler networks and hope that this also helps to emphasize these results.

		Lines 379-389:

		\begin{quotation}

			Such approaches are particularly useful when considering interactions involving species entering new ranges due to climate change or introductions. Our framework could, for example, be used to predict the probability of interaction between a galler and parasitoid at a new site on the frontier of their ranges. If the species have not been observed co-occurring at other sites, we would expect them to interact with a probability of approximately 0.1 rather than assuming that they will not interact because they have not been observed interacting elsewhere (Fig. 3). Understanding species' interactions in novel or changing communities is important for a variety of conservation questions~\citep{Bartomeus2013,Gravel2013}, and a Bayesian approach using a trait-matching model or data from species' current ranges could help us to anticipate how species will integrate into new communities.

@@

		Finally, we must disagree with the Reviewer's contention that ``empirical Bayes assumes a kind of commonality among all networks". This is not so; empirical Bayes only assumes some commonality between the focal network and those used to construct the prior. We have revised the text to emphasize the need to use similar networks to construct an empicial Bayes prior and note that \emph{Appendix S7} demonstrates the pitfalls of basing an empirical Bayes prior on a network with little commonality with the focal system.

		We believe that including an expanded reference to \emph{Appendix S7} as suggested below will help to address some of these concerns by demonstrating that empirical Bayes should \emph{not} be based on networks which have major differences from the focal system as this will lead to unreasonable predictions (in our case, although the taxa and interaction types involved were similar, the taxonomic resolution in the \citet{Barbour2016} and \citet{Kopelke2017} were very different). To reinforce this point and make the role of empirical Bayes as a solution in the absence of trait-based models and/or trait information, we have made several minor revisions to the section introducing informative priors. We hope that these changes will be sufficient to illustrate the drawbacks to empirical Bayes without being overly discouraging for those who lack the necessary information to construct more detailed informative priors.

		In lines 258-262 we state that empirical Bayes is an option if information about traits is lacking but that an empirical Bayes prior does not vary between species pairs:

@@

		\begin{quotation}

			Alternatively, if information on the traits affecting interaction probabilities is lacking, one can develop a prior based on the properties of a set of published networks (``empirical" or ``reference Bayes"~\citet{Spiegelhalter2000}). This type of prior does not vary between species pairs but entails only one assumption: that the focal network has similar structural properties to those of some published networks.

		\end{quotation}

		In lines 264-266 we explicitly state that the networks used to build an empirical Bayes prior should be similar to the focal system:

@@

		\begin{quotation}

			The distribution of published connectances can be used to predict the distribution of interaction probabilities in a new network that is similar to those used to construct the prior (same type of interaction, similar taxonomic resolution, habitat, etc.).

		\end{quotation}

		In lines 269-272 we reiterate the fact that an empirical Bayes prior does not vary between pairs of species and that the networks used to build the prior should be similar to the focal network. We also acknowledge the possibility that published data are derived from under-sampled data and therefore will underestimate interaction probabilities

@@

		\begin{quotation}

		Note that here the prior distribution will be the same for all interaction probabilities. It is also possible to interpret other network properties (e.g., species degrees) in a similar network(s) as interaction probabilities and use these to create a prior (worked example in \emph{Appendix S4}).

		\end{quotation}

		Finally, please note that we do discuss caveats to the empirical Bayes approach in lines 272-281, including the possibility that priors based on substantailly different systems will be misleading (with reference to \emph{Appendix S7}) and that published data may reflect under-sampled data:

			When using network summary statistics or degree distributions, it is important to consider whether the available information reflects what we believe about the network. Given the likelihood that most published networks are undersampled~\citep{Jordano2016}, it may be wise to include only the highest-quality networks available in a prior. Likewise, only the degree distribution for a similar system is likely to be a reasonable prior for a focal system. For example, if the focal system is large and contains a diverse array of species, it would be inappropriate to use a prior distribution drawn from a small network describing closely-related taxa (demonstrated in \emph{Appendix S7}). Similarly, data from a network where nodes are resolved to different taxonomic levels than the focal network are likely to have quite different properties and would not be an appropriate prior.

	3. Include material from \emph{Appendix 7} in the main text

@@

		\textbf{R:} This material was indeed placed in an appendix because of space constraints. We have added a figure showing the posterior distributions obtained from both priors and a paragraph summarizing \emph{Appendix 7}. As we do not wish to be too demanding with regard to extra space (and our manuscript was essentially at the standard length limit after the last revision), we hope that these smaller additions will be enough to emphasize the potential for spurious results after poor prior choices. Also note that the results for the galler-parasitoid community were somewhat similar. In order to more clearly demonstrate the potentially large effects of prior choice, we therefore showcase the results from \emph{Salix}-galler networks in this paragraph.

		Lines 390-405:

		\begin{quotation}

		  Note that, as in all Bayesian analyses, our results do depend on the prior chosen. To demonstrate this, we repeated our analyses using a prior derived from a study of gallers found on several genotypes of \emph{Salix hookeriana} and the parasites which emerged from them (\citealp{Barbour2016,Barbour2016Dryad}; \emph{Appendix S7}). Although the study system is similar to that in~\citet{Kopelke2017}, the network is quite different due to using different genotypes of a single \emph{Salix} species rather than several \emph{Salix} species as the basis for sampling. While this had a relatively small effect on our expectations for the galler-parasitoid community (\emph{Appendix S7}), the prior based on \citep{Barbour2016} resulted in very high probabilities of interaction between \emph{Salix} and galler pairs that were not observed interacting (Fig. 4). No amount of additional sampling would allow us to conclude that a given \emph{Salix}-galler pair did not interact with a threshold interaction probability of 0.01. This is reasonable for the situation described in~\citet{Barbour2016}, as it is very likely that gallers which can interact with one \emph{S. hookeriana} genotype can interact with most others, but is not reasonable for the more diverse community in~\citet{Kopelke2017}. This demonstrates the importance of conducting a "sanity check" on the posterior distribution obtained from any given prior.

### 2019-02-21 manuscript/CI_interactions.tex
updated text, reply

        We often have some prior knowledge which can inform uncertainty about interactions. One common example is the well-justified assumption that plants never consume animals in a food web; excluding carnivorous plants it is not contentious to say that we are certain that unobserved links indicating plants feeding on animals truly do not occur. Similarly, if we observed two species which are normally obligate mutualists co-occurring but not interacting, we would be very doubtful that a zero reflecting this interaction was true (i.e., high uncertainty about this zero). It is straightforward to extend the intuition behind these special cases to the full set of species in a network using trait-based models if the traits likely to affect interaction probabilities are known (e.g.,~\citet{Gravel2013,Bartomeus2016,Weinstein2017}). Informative models could also include information on abundances, phenological matching, co-occurrence, etc. as available~\citep{Jordano2016,Weinstein2017a,s,Gravel2018}. Multiple sources of information can be combined into a single model (e.g., the the $K$ nearest neighbour (KNN) algorithm, which identifies likely interaction partners based on similarity to known partners~\citep{DesjardinsProulx2017}). This would result in a highly informative prior that would, moreover, account for some of the non-independence in interaction probabilities.

@@

        Alternatively, one can develop a prior based on the properties of a set of published networks (``empirical" or ``reference Bayes"~\citet{Spiegelhalter2000}). This type of prior entails only one assumption: that the focal network has similar structural properties to those of some published networks. For example, connectance ($C=N/S^2$, where $N$ is the number of interactions and $S$ is the number of species) is available for many networks. The distribution of published connectances can be used to predict the distribution of interaction probabilities in a new network that is similar to those used to construct the prior (same type of interaction, similar taxonomic resolution, habitat, etc.). If we know the mean $\overline{C}$ and variance $\sigma_C^2$ of a distribution of connectances, then the hyperparameters are:

@@

        Note that if the focal network is substantially different from published networks, empirical Bayes will not give reasonable expectations about interaction probabilities in the focal network. [[Seems like R1 is demanding we add some more about how empirical Bayes is crap ... maybe we can say it'd give a reasonable expectation for the number of interactions but maybe not the right ones?]]

@@

\captionsetup{singlelinecheck=false, font={stretch=2}}

>>>>

        We often have some prior knowledge which can inform uncertainty about interactions. One common example is the well-justified assumption that plants never consume animals in a food web; excluding carnivorous plants it is not contentious to say that we are certain that unobserved links indicating plants feeding on animals truly do not occur. Similarly, if we observed two species which are normally obligate mutualists co-occurring but not interacting, we would be very doubtful that a zero reflecting this interaction was true (i.e., high uncertainty about this zero). It is straightforward to extend the intuition behind these special cases to the full set of species in a network using trait-based models if the traits likely to affect interaction probabilities are known (e.g.,~\citet{Gravel2013,Bartomeus2016,Weinstein2017}). Informative models could also include information on abundances, phenological matching, co-occurrence, etc. as available~\citep{Jordano2016,Weinstein2017a,Gravel2018}. Multiple sources of information can be combined into a single model (e.g., the the $K$ nearest neighbour (KNN) algorithm, which identifies likely interaction partners based on similarity to known partners~\citep{DesjardinsProulx2017}). This would result in a highly informative prior that would, moreover, account for some of the non-independence in interaction probabilities.

@@

        Alternatively, if information on the traits affecting interaction probabilities is lacking, one can develop a prior based on the properties of a set of published networks (``empirical" or ``reference Bayes"~\citet{Spiegelhalter2000}). This type of prior does not vary between species pairs but entails only one assumption: that the focal network has similar structural properties to those of some published networks. For example, connectance ($C=N/S^2$, where $N$ is the number of interactions and $S$ is the number of species) is available for many networks. The distribution of published connectances can be used to predict the distribution of interaction probabilities in a new network that is similar to those used to construct the prior (same type of interaction, similar taxonomic resolution, habitat, etc.). If we know the mean $\overline{C}$ and variance $\sigma_C^2$ of a distribution of connectances, then the hyperparameters are:

@@

@@

% \captionsetup{singlelinecheck=false, font={stretch=2}}
